\anonsection{Список использованной литературы}
{\def\section*#1{}
\begin{thebibliography}{99}
\bibitem{Yee} Yee,\,K. Numerical solution of initial boundary value problems involving
Maxwell’s equations in isotropic media /~K,Yee //~Antennas and Propagation, IEEE Transactions. --~1966. --~Vol.~14, no.~3. --~P.~302--307.
\bibitem{Schneider} Schneider\,J.\,B. Understanding the Finite-Difference Time-Domain Method /~J.\,B.\,Schneider. //~Understanding the FDTD Method : [сайт]. ---~ URL: http://www.eecs.wsu.edu/\textasciitilde{}schneidj/ufdtd/ (дата обращения: 12.06.2017).
\bibitem{Berenger94}Berenger\,J.-P.~A perfectly matched layer for the absorption of electromagnetic waves /~J.-P.\,Berenger //~Journal of Computational Physics --~1994. --~No~2 --~P.~185--200. 
\bibitem{Taflove2005} Taflove\,A. Computational Electrodynamics: The Finite-Difference Time-Domain Method /~A.\,Taflove, S.\,C.\,Hagness. ---~3rd ed. ---~ARTECH HOUSE, INC., 2005. ---~1037 p.
\bibitem{Berenger} Berenger\,J.-P.~Improved PML for the FDTD solution of wave-structure interaction problems /~J.-P.\,Berenger //~IEEE Transactions on Antennas and Propagation --~1997. --~Vol.~45 --~P. 466--473.
\bibitem{Makinen} Makinen\,R.\,M.~A stabilized resistive voltage source for FDTD thin-wire models /~R.\,M.\,Makinen, M.\,A.\,Kivikovski //~IEEE Transactions on Antennas and Propagation --~2003. --~Vol.~51 --~P. 1615--1622.
\bibitem{Berillo} Берилло\,А. Nvidia CUDA --- неграфические вычисления на графических процессорах /~А.\,Берилло //~ URL: http://www.ixbt.com/video3/cuda-1.shtml  (дата обращения: 12.06.2017).
\bibitem{Galoppo} Galoppo\,N.~LU-GPU: Efficient algorithms for solving dense linear systems on graphics hardware /~N. Galoppo [et al.] //~Proceedings - Thirteenth International Symposium on Temporal Representation and Reasoning, TIME 2006. -- Seatle, WA,~2005. -- P.~3--15.
\bibitem{CUDADoc} Programming Guide :: CUDA Toolkit Documentation : [сайт]. ---~URL: http://docs.nvidia.com/cuda/cuda-c-programming-guide/index.html (дата обращения: 12.06.2017).
\bibitem{Frolov} Фролов\,В. Введение в технологию CUDA /~В.\,Фролов //~Компьютерная графика и мультимедиа :~электрон. журн. --~2008. --~No~6 (дек.). --~URL: http://www.webcitation.org/65tg9Hcl3 (дата обращения: 15.06.2017).
\end{thebibliography}
}
\clearpage
